\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}   
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}	
\usepackage{msc}

% Setting for MSC diagrams
\setlength{\levelheight}{0.6cm}
\setlength{\instdist}{4.5cm}
\setlength{\actionwidth}{1.5cm}


\author{
Lesly-Ann Daniel \and Benjamin Fasquelle \and Rémi Hutin\\
}
\title{
Attack on: or 1=1\\
From group \textsc{BALEC}
}

\setlength\parindent{0pt}

\begin{document}
\maketitle


\section{Description of the Attack}
\begin{table}[!h]
\centering
\begin{tabular}{lll}
$Bob \rightarrow Eve:$ & $ \{Bob,K\}pk(Eve) $\\
$Eve(Bob) \rightarrow Alice:$ & $ \{Bob,K\}pk(Alice) $ &\\
$Alice \rightarrow Bob:$ & $ \{ h(K),N \}pk(Bob) $ & \#intercepted \\ 
$Eve \rightarrow Bob:$ & $ \{ h(K),N \}pk(Bob) $ & \\
$Bob \rightarrow Eve:$ & $ N $ &\\
$Eve(Bob) \rightarrow Alice:$ & $ N $ &\\
\end{tabular}
\end{table}

\paragraph{Man in the Middle Attack}
Alice and Bob are honest agents and Eve is dishonest.
\begin{itemize}
 \item Bob initiates a connexion with Eve.
 \item Eve initiates a connexion with Alice, pretending that she is Bob.
 \item Alice respond to Bob with an encrypted nonce \(N\) with Bob's public key. This message is intercepted by the attacker.
 \item Eve reuses this encrypted nonce and sends it to Bob to pursue her session of the protocol.
 \item Bob sends the decrypted nonce back to Eve.
 \item Eve can terminate the protocol with Alice by sending the decrypted nonce, pretending she is Bob.
\end{itemize}

In this attack, Alice terminates the execution of the protocol thinking that she communicated with Bob, when she actually communicated with Eve. The {\em secrecy} of the key $K$ is violated since it is known by the attacker. The {\em agreement} is also violated since the messages received by Alice from Bob were not sent by Bob.

% \begin{figure}[!ht]
% \centering
% \begin{msc}{Protocole}
%   \declinst{A}{$A$}{}
%   \declinst{B}{$B$}{}
%   \nextlevel
%   \action{secret $K$}{A}
%   \nextlevel[2]
%   \mess{$\langle h(A, K), \{K\}_{pk(B)} \rangle $}{A}{B}
%   \nextlevel
%   \action{nonce $n$}{B}
%   \nextlevel[2]
%   \mess{$\langle h(B, K, n), \{n\}_{pk(A)} \rangle $}{B}{A}
%   \nextlevel
%   \mess{$h(n)$}{A}{B}
%   \nextlevel
% \end{msc}
% \end{figure}

\end{document}
