\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}   
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyvrb}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}	
\usepackage{msc}

% Setting for MSC diagrams
\setlength{\levelheight}{0.6cm}
\setlength{\instdist}{4.5cm}
\setlength{\actionwidth}{1.5cm}


\author{
Lesly-Ann Daniel \and Benjamin Fasquelle \and Rémi Hutin\\
}
\title{
Attack on: Gros Pigeons v1\\
From group \textsc{BALEC}
}

\setlength\parindent{0pt}

\begin{document}
\maketitle


\section{Description of the Attack}
\begin{table}[!h]
\centering
\begin{tabular}{lll}
Session 1 & I=Bob , R=Alice &\\
$Bob \rightarrow Alice:$ & $\{K,Bob\}pk(Alice)$ & \\
$Alice \rightarrow Bob:$ & $ h(K),\{N1,Alice\}pk(Bob))$ & \#intercepted\\
\\
Session 2 & I=Charlie(Bob) , R=Alice &\\
$Charlie(Bob)\rightarrow Alice:$ & $ \{K',Bob\}pk(Alice)$ & \\
$Alice \rightarrow Bob:$ & $ h(K'),\{N2,Alice\}pk(Bob))$ & \#intercepted\\
\\
Attack & &\\
$Charlie(Alice)\rightarrow Bob:$ & $ (h(K),\{N2,Alice\}pk(Bob)) $\\ 
$Bob \rightarrow Alice:$ & $h(N2)$\\
\end{tabular}
\end{table}

\paragraph{Description}
Alice and Bob are honest agents and Charlie is dishonest.
\begin{itemize}
 \item Bob generates a secret \(K\) and initiates a connexion with Alice.
 \item Alice generates the nonce \(N1\) for Bob and sends it to him. The message is intercepted.
 \item Charlie generates a secret \(K'\) and initiates a connexion with Alice pretending he is Bob.
 \item Alice generates a nonce \(N2\) and answers to this message. Her response is intercepted.
 \item Charlie uses the knowledge he acquired from the messages 2 and 4 to build a new message for Bob. He reuses the \(h(K)\) calculated by Alice in message 2. He replaces the Nonce \(N1\) from the second message with the nonce \(N2\) encrypted by Alice with Bob's public key.
 \item Finally, Bob thinking that the nonce \(N2\) is the correct nonce and that the message comes from Alice, he sends back the hash of the nonce \(N2\) to Alice.
 \item When Alice receives the message $h(N2)$, associated with the execution initiated by Charlie pretending to be Bob, she accepts the secret \(K'\) generated by the intruder.
\end{itemize}

In this attack, Alice terminates the execution of the protocol thinking that she communicated with Bob. Actually she communicated with Charlie and accepted the secret \(K'\) generated by the intruder, violating the {\em secrecy} of \(K\).

% \begin{figure}[!ht]
% \centering
% \begin{msc}{Protocole}
%   \declinst{A}{$A$}{}
%   \declinst{B}{$B$}{}
%   \nextlevel
%   \action{secret $K$}{A}
%   \nextlevel[2]
%   \mess{$\langle h(A, K), \{K\}_{pk(B)} \rangle $}{A}{B}
%   \nextlevel
%   \action{nonce $n$}{B}
%   \nextlevel[2]
%   \mess{$\langle h(B, K, n), \{n\}_{pk(A)} \rangle $}{B}{A}
%   \nextlevel
%   \mess{$h(n)$}{A}{B}
%   \nextlevel
% \end{msc}
% \end{figure}

\end{document}
